Computable Poincar\'e--Friedrichs constants\\ for the $L^{p}$ de Rham complex over domains\\ with shellable triangulations

### 2024-09-09 main.tex
additional construction

>>>>

        \item 
        Consider any $n$-simplex $R \in \calR$ and let $R^c \in \calR^{c}$ be its image under $\Theta$.
        We construct a bi-Lipschitz mapping 
        \begin{align*}
            \Gamma_{R} : R \cup R^{c} \rightarrow R^{c}
        \end{align*}
        and analyze its properties. The construction will be such that the union of $\Gamma_{R}$ for all $n$-simplices $R \in \calR$
        will define a bi-Lipschitz mapping 
        \begin{align*}
            \Gamma : \underlying{\calR'} \rightarrow \underlying{\calR^{c}}
        \end{align*}
        which will be the identity along $\partial\underlying{\calR'} \setminus \partial\underlying{\calR}$.

        We write $h_{z}$ for the height of $z_{S'}$ within $K$.
        Given $x \in K \cup K^{c}$, we can write uniquely
        \begin{align*}
            x = t z_{S} + x^{\perp}, \quad t \in [-1,1], \quad x^{\perp} \in K \cap K^{c}.
        \end{align*}
        Notice that 
        \begin{align*}
            t = \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} 
        \end{align*}
        We define 
        \begin{align*}
            \Gamma_{K}(x) = x - \frac 1 2 \left( \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} - 1 \right) z_{S'}
        \end{align*}
        We readily verify that this transformation satisfies the desired properties. 
        It remains to analyze its Jacobian.

        We have an orthogonal decomposition $h_{z} + b_{z} = z_{S'}$.
        With that,
        \begin{align*}
            \Jacobian \Gamma_{K}(x)
            &=
            \Id 
            - 
            \frac{1}{ 2 \langle h_{z},z_{S'}\rangle } 
            z_{S'} \otimes h_{z}^{t}
            =
            \Id 
            - 
            \frac{1}{ 2 \langle h_{z},z_{S'}\rangle }  
            z_{S'} \otimes h_{z}^{t}
            \\
            &=
            \Id 
            - 
            \frac{1}{ 2 \langle h_{z},z_{S'}\rangle } 
            h_{z} \otimes h_{z}^{t}
            - 
            \frac{1}{ 2 \langle h_{z},z_{S'}\rangle } 
            b_{z} \otimes h_{z}^{t}
            \\
            &=
            \Id 
            - 
            \frac{1}{ 2 } 
            \hat h_{z} \otimes \hat h_{z}^{t}
            - 
            \frac{ \|b_z\| }{ 2 \| h_{z} \| } 
            \hat b_{z} \otimes \hat h_{z}^{t}
            .
        \end{align*}
        We write $\beta$ for the angle between $h_{z}$ and $z_{S'}$.
        Hence $\tan(\beta) = \| b_z \| / \| h_z \|$. It remains to study the singular values of the matrix 
        \begin{align*}
            C 
            = 
            \frac 1 2 
            \begin{pmatrix}
                1 & 0 
                \tan(\beta) & 2 
            \end{pmatrix}
        \end{align*}
        By building the symmetric matrix $C^{t} C$ and computing its eigenvalues, we obtain 
        \begin{align*}
            \sigma_{\max} = \sqrt{ \frac{ \tan(\beta)^{2} + 5 }{8} + \frac 1 8 \sqrt{ \tan(\beta)^{4} + 10 \tan(\beta)^{2} + 9 } }
            ,
            \\
            \sigma_{\min} = \sqrt{ \frac{ \tan(\beta)^{2} + 5 }{8} - \frac 1 8 \sqrt{ \tan(\beta)^{4} + 10 \tan(\beta)^{2} + 9 } }
            .
        \end{align*}
        These are also the maximal and minimal eigenvalues of the Jacobian $\Jacobian \Gamma$,
        the remaining eigenvalues being equal to $1$. Upon close inspection, we see that 
        \begin{align*}
            \sigma_{\max} = \frac 1 4 \sqrt{ 9 + \tan(\beta)^2 } + \frac 1 4 \sqrt{ 1 + \tan(\beta)^2 }
            ,
            \\
            \sigma_{\min} = \frac 1 4 \sqrt{ 9 + \tan(\beta)^2 } - \frac 1 4 \sqrt{ 1 + \tan(\beta)^2 }
            .
        \end{align*}
        These are monotonely increasing and decreasing, respectively, in $\tan(\beta)$. 
        Moreover, $\sigma_{\max} \sigma_{\min} = 1/2$. 
        We now recall that the height of $h_{z}$ in $K \in \calR$ equals $(k+1)^{-1}$ multiplied with the height of some vertex of $S$ within $T$.
        Similar as above, we use the upper bound 
        \begin{align*}
            \tan(\beta) = \frac{\|b_z\|}{\|h_z\|} \leq (k+1) \mu(T).
        \end{align*}
        We conclude that 
        \begin{gather*}
            \| \Jacobian\Gamma \| 
            \leq 
            \frac 1 4 \sqrt{ 9 + (k+1)^2 \mu(T)^2 } + \frac 1 4 \sqrt{ 1 + (k+1)^2 \mu(T)^2 }
            ,
            \\
            \| \Jacobian\Gamma^{-1} \| 
            \leq 
            \frac 1 2 \sqrt{ 9 + (k+1)^2 \mu(T)^2 } + \frac 1 2 \sqrt{ 1 + (k+1)^2 \mu(T)^2 }
            \\
            \det \Jacobian\Gamma = \frac 1 2 
            .
        \end{gather*}
